Project 2

### 2021-10-09 project_2.Rmd
plot

```{r fitzgerald_emotion_table}
#counting how often female words appeared
#table shows each text and the respective percentage
fitzgerald_emotion_calc <- fitzgerald_emotions %>% group_by(title) %>% count(emotion) %>% mutate(percent = n/sum(n)*100)

@@

```{r hemingway_emotion_table}
#counting how often female words appeared
#table shows each text and the respective percentage
hemingway_emotion_calc <- hemingway_emotions %>% group_by(title) %>% count(emotion) %>% mutate(percent = n/sum(n)*100)

@@

>>>>

```{r fitzgerald_emotion_table}
#counting how often female words appeared
#table shows each text and the respective percentage
fitzgerald_emotion_calc <- fitzgerald_emotions %>% group_by(title) %>% count(emotion) %>% mutate(percent = n/sum(n)*100) %>% mutate(author = "F. Scott Fitzgerald")

@@

```{r hemingway_emotion_table}
#counting how often female words appeared
#table shows each text and the respective percentage
hemingway_emotion_calc <- hemingway_emotions %>% group_by(title) %>% count(emotion) %>% mutate(percent = n/sum(n)*100) %>% mutate(author = "Earnest Hemingway")

@@

```{r emotion_plot}
combined_table <- bind_rows(hemingway_emotion_calc, fitzgerald_emotion_calc) %>% filter(emotion == TRUE)

p<-ggplot(data=combined_table, aes(x=percent, y=title, fill=author)) +
  geom_bar(stat="identity")
p
```
